Output Summary

### 2023-05-03 03-post-process/output-plots-children/04-egg-to-parr-surv.Rmd
Consistency updates: 04-fit-to-data.Rmd

## Survival Time Series

```{r phi_E_Pb-plots, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_E_Pb[year,pop]$", year = ts_yrs, pop = j)),
               yrs = all_yrs[ts_yrs],
               main = pops[j])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Egg-to-Parr Survival")
```

@@

```{r egg-surv-vs-eggs, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  # extract posterior samples of the BH productivity and capacity parameters
  alpha = post_subset(post, sub_index("alpha[pop]", pop = j), matrix = TRUE)
  beta = post_subset(post, sub_index("beta[pop]", pop = j), matrix = TRUE)

@@

  # graphical parameters
  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))

  # empty plot
  plot(1, 1, type = "n", xlim = range(0, E[5,]), ylim = range(0, phi_E_Pb[5,], phi_E_Pb_pred[5,]),
       xlab = "", ylab = "", xaxt = "n", yaxt = "n", main = pops[j])

@@

  # draw fitted relationship
  polygon(c(E_pred, rev(E_pred)), c(phi_E_Pb_pred[4,], rev(phi_E_Pb_pred[5,])), col = alpha("salmon", 0.5), border = NA)
  lines(phi_E_Pb_pred[4,] ~ E_pred, col = "red", lty = 2)
  lines(phi_E_Pb_pred[5,] ~ E_pred, col = "red", lty = 2)
  lines(phi_E_Pb_pred[3,] ~ E_pred, col = "red", lwd = 2)

  # draw state pairs + uncertainty
  segments(E[4,], phi_E_Pb[3,], E[5,], phi_E_Pb[3,], col = alpha("red", 0.5))
  segments(E[3,], phi_E_Pb[4,], E[3,], phi_E_Pb[5,], col = alpha("red", 0.5))
  points(phi_E_Pb[3,] ~ E[3,], pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
  text(phi_E_Pb[3,] ~ E[3,], labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Total Egg Production (Millions)")
mtext(side = 2, outer = T, line = 0.25, "Egg-to-Parr Survival")
```

@@

```{r eggs-to-parr, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  # extract posterior samples of the BH productivity and capacity parameters
  bh_params = post_subset(post, sub_index(c("alpha[pop]", "^beta[pop]$"), pop = j), matrix = TRUE)

  # extract posterior summaries of total spawners by brood year
  # Sa_tot = post_summ(post, sub_index("^Sa_tot[year,pop]", pop = j, year = ts_yrs))

@@

  # predict parr recruits along a sequence of spawner abundances
  # Sa_pred = seq(0, max(Sa_tot[5,]), length = 30)
  E_pred = seq(0, max(E[5,]), length = 30)

@@

  # graphical parameters
  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))

  # empty plot
  plot(1, 1, type = "n", xlim = range(0, E[5,]), ylim = range(0, Pb[5,], Pb_pred[5,]),
       xlab = "", ylab = "", xaxt = "n", yaxt = "n", main = pops[j])

@@

  # draw fitted relationship: Bayesian
  polygon(c(E_pred, rev(E_pred)), c(Pb_pred[4,], rev(Pb_pred[5,])), col = alpha("salmon", 0.5), border = NA)
  lines(Pb_pred[4,] ~ E_pred, col = "red", lty = 2)
  lines(Pb_pred[5,] ~ E_pred, col = "red", lty = 2)
  lines(Pb_pred[3,] ~ E_pred, col = "red", lwd = 2)

  # draw state pairs + uncertainty
  segments(E[4,], Pb[3,], E[5,], Pb[3,], col = alpha("red", 0.5))
  segments(E[3,], Pb[4,], E[3,], Pb[5,], col = alpha("red", 0.5))
  points(Pb[3,] ~ E[3,], pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
  text(Pb[3,] ~ E[3,], labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Total Egg Production (Millions)")
mtext(side = 2, outer = T, line = 0.25, "Parr Recruits (Thousands)")
```

@@

```{r eggs-vs-spawners, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  # extract posterior summaries of total spawners by brood year
  Sa_tot = post_summ(post, sub_index("^Sa_tot[year,pop]", pop = j, year = ts_yrs))

@@

  # graphical parameters
  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))

  # empty plot
  plot(E["mean",] ~ Sa_tot["mean",],
       ylim = c(0, max(E["97.5%",])),
       xlim = c(0, max(Sa_tot["97.5%",])), type = "n",
       ylab = "", xlab = "", las = 1, yaxt = "n")

@@

  segments(Sa_tot["2.5%",], E["mean",], Sa_tot["97.5%",], E["mean",], col = alpha("red", 0.5))
  segments(Sa_tot["mean",], E["2.5%",], Sa_tot["mean",], E["97.5%",], col = alpha("red", 0.5))
  points(E["mean",] ~ Sa_tot["mean",], pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
  text(E["mean",] ~ Sa_tot["mean",], labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")

@@

  if (j == 1) {
    legend("bottomright", title = "If Each Spawner Had:",
           legend = c("1000 Eggs", "1800 Eggs", "3600 Eggs"),
           lty = c(1,2,3), bty = "n", cex = 0.75)
  }
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Total Spawners")
mtext(side = 2, outer = T, line = 0.25, "Total Egg Production (Millions)")
```

>>>>

## Survival Time Series {.tabset .tabset-pills}

These figures show the realized time series of egg-to-parr survival that include all sources of variability in red: that explained by Beverton-Holt dynamics and that not explained by it.

### Realized Alone

Just the realized time series shown.

```{r phi_E_Pb-plots, fig.width = p4_width, fig.height = p4_height}
# function to create the plot for one population
plot_f = function(j) {
  # realized time series
  plot_tseries(est = post_summ(post, sub_index("^phi_E_Pb[year,pop]$", year = ts_yrs, pop = j)),
               yrs = all_yrs[ts_yrs], label_text = pops[j])
}

# loop over populations
mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Egg \u2192 Parr Survival")
```

### Realized & BH

The blue shows the time series with variability explained only by Beverton-Holt dynamics.

```{r phi_E_Pb_dot-plots, fig.width = p4_width, fig.height = p4_height}
# function to create the plot for one population
plot_f = function(j) {
  # realized time series
  plot_tseries(est = post_summ(post, sub_index("^phi_E_Pb[year,pop]$", year = ts_yrs, pop = j)),
               yrs = all_yrs[ts_yrs], label_text = pops[j])

  # time series that includes BH prediction only
  add_tseries(post_summ(post, sub_index("^phi_E_Pb_dot[year,pop]", year = ts_yrs, pop = j)),
              yrs = all_yrs[ts_yrs])
}

# loop over populations
mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Egg \u2192 Parr Survival")
```

### Realized & [BH + AR(1)]

The blue shows the time series with variability explained by Beverton-Holt dynamics and the carry-over residual.

```{r phi_E_Pb_dot2-plots, fig.width = p4_width, fig.height = p4_height}
# function to create the plot for one population
plot_f = function(j) {
  # realized time series
  plot_tseries(est = post_summ(post, sub_index("^phi_E_Pb[year,pop]$", year = ts_yrs, pop = j)),
               yrs = all_yrs[ts_yrs], label_text = pops[j])

  # time series that includes BH prediction only
  add_tseries(post_summ(post, sub_index("^phi_E_Pb_dot2[year,pop]", year = ts_yrs, pop = j)),
              yrs = all_yrs[ts_yrs])
}

# loop over populations
mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Egg \u2192 Parr Survival")
```

@@

```{r egg-surv-vs-eggs, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {
  # extract posterior samples of the BH productivity and capacity parameters
  alpha = post_subset(post, sub_index("alpha[pop]", pop = j), matrix = TRUE)
  beta = post_subset(post, sub_index("beta[pop]", pop = j), matrix = TRUE)

@@

  # empty plot
  plot(1, 1, type = "n", xlim = range(0, E["97.5%",]),
       ylim = range(0, phi_E_Pb["97.5%",], phi_E_Pb_pred["97.5%",]),
       xlab = "", ylab = "", xaxt = "n", yaxt = "n")

  # add panel label
  panel_label(pops[j], "topright")

@@

  # draw fitted relationship
  polygon(c(E_pred, rev(E_pred)), c(phi_E_Pb_pred["2.5%",], rev(phi_E_Pb_pred["97.5%",])), col = tran_cols["model"], border = NA)
  lines(phi_E_Pb_pred["mean",] ~ E_pred, col = main_cols["model"], lwd = 2)

  # draw state pairs + uncertainty
  segments(E["2.5%",], phi_E_Pb["mean",], E["97.5%",], phi_E_Pb["mean",], col = main_cols["model"])
  segments(E["mean",], phi_E_Pb["2.5%",], E["mean",], phi_E_Pb["97.5%",], col = main_cols["model"])
  points(phi_E_Pb["mean",] ~ E["mean",], pch = 16, col = tran_cols["model"], cex = 1.8)
  text(phi_E_Pb["mean",] ~ E["mean",], labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
}

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Total Egg Production (Millions)", "Egg \u2192 Parr Survival")
```

@@

```{r eggs-to-parr, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {
  # extract posterior samples of the BH productivity and capacity parameters
  bh_params = post_subset(post, sub_index(c("alpha[pop]", "^beta[pop]$"), pop = j), matrix = TRUE)

@@

  # predict parr recruits along a sequence of spawner abundances
  E_pred = seq(0, max(E[c("2.5%", "97.5%"),]), length = 30)

@@

  # empty plot
  plot(1, 1, type = "n", xlim = range(0, E["97.5%",]), ylim = range(0, Pb["97.5%",], Pb_pred["97.5%",]),
       xlab = "", ylab = "", xaxt = "n", yaxt = "n")

  panel_label(pops[j])

@@

  # draw fitted relationship: Bayesian
  polygon(c(E_pred, rev(E_pred)), c(Pb_pred["2.5%",], rev(Pb_pred["97.5%",])), col = tran_cols["model"], border = NA)
  lines(Pb_pred["mean",] ~ E_pred, col = main_cols["model"], lwd = 2)

  # draw state pairs + uncertainty
  segments(E["2.5%",], Pb["mean",], E["97.5%",], Pb["mean",], col = main_cols["model"])
  segments(E["mean",], Pb["2.5%",], E["mean",], Pb["97.5%",], col = main_cols["model"])
  points(Pb["mean",] ~ E["mean",], pch = 16, col = tran_cols["model"], cex = 1.8)
  text(Pb["mean",] ~ E["mean",], labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
}

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Total Egg Production (Millions)", "Parr Recruits (Thousands)")
```

@@

```{r eggs-vs-spawners, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {
  # extract posterior summaries of total spawners by brood year
  Sa_tot = post_summ(post, sub_index("^Sa_tot[year,pop]", pop = j, year = ts_yrs))

@@

  # empty plot
  plot(E["mean",] ~ Sa_tot["mean",],
       ylim = c(0, max(E["97.5%",])),
       xlim = c(0, max(Sa_tot["97.5%",])), type = "n",
       ylab = "", xlab = "", yaxt = "n")
  panel_label(pops[j])

@@

  segments(Sa_tot["2.5%",], E["mean",], Sa_tot["97.5%",], E["mean",], col = main_cols["model"])
  segments(Sa_tot["mean",], E["2.5%",], Sa_tot["mean",], E["97.5%",], col = main_cols["model"])
  points(E["mean",] ~ Sa_tot["mean",], pch = 16, col = tran_cols["model"], cex = 1.8)
  text(E["mean",] ~ Sa_tot["mean",], labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")

@@

  if (j == 1) {
    legend("bottomright", title = "Eggs/Spawner:",
           legend = c("1,000", "1,800", "3,600"),
           lty = c(1,2,3), bty = "n", cex = 0.75)
  }
}

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Total Spawners", "Total Egg Production (Millions)")
```

### 2023-05-03 03-post-process/output-plots.Rmd
Consistency updates: 04-fit-to-data.Rmd

```{r setup, include = FALSE}
# set global knitting options
knitr::opts_chunk$set(echo = FALSE, fig.align = "center")

@@

```{r set-plot-opts}
# select main colors
main_cols = c(
  "model" = "salmon",
  "model2" = "forestgreen",
  "data" = "royalblue"
)

>>>>

```{r setup, include = FALSE}
# set global knitting options
knitr::opts_chunk$set(echo = FALSE, fig.align = "center", dpi = 600, out.width = "75%")

@@

```{r set-plot-opts}
# select main colors
main_cols = c(
  "model" = "salmon",
  "model2" = "royalblue",
  "data" = "royalblue"
)
